---
title: "Assignment-b1-v3"
output: github_document
date: "2023-11-03"
---
*Stats 545B Assignment B-1*

The code and explanations following are intended to fulfil requirements for Stats545B assignment B-1.

*Packages to load*
```{r}
library(tidyverse)
library(testthat)
library(dplyr)
library(gapminder)
library(digest)
library(palmerpenguins)
library(commonmark)
library(devtools)
library(roxygen2)
```

*Exercise 1: Make a Function, & Exercise 2: Document your Function*

This is a simple function designed to quickly return some simple summary statistics.
```{r}
#' Generate Summary Statistics
#'
#' @description This function allows you to produce simple summary statistics for numeric variables. The summary statistics returned are range, mean, and median.
#'
#' @param x A numeric variable of interest
#'
#' @return Range, mean, and median
#'
#' @examples
#' summary_stats(penguins$bill_length_mm)
#' summary_stats(gapminder$lifeExp)
summary_stats <- function(x){
  if(!is.numeric(x)) {
    stop('Input is not of class numeric: Input must be of class numeric')}
  range <- max(x) - min(x)
  mean <- mean(x)
  median <- median(x)
  return(c(range, mean, median))
}
```

*Exercise 3: Include Examples*

Example 1:

Here is an example using the palmerspenguins::penguins dataset. Here, I filter penguins to only include the adelie species, then drop na values. Finally, I put the new dataset through the summary_stats function to return summary statistics about the adelie species' bill length.
```{r}
adelie <- penguins %>%
  filter(species == "Adelie") %>%
  drop_na()

summary_stats(adelie$bill_length_mm)
```
Example 2:

Here is an example using the gapminder::gapminder dataset. In this example, I filter gapminder to only include European countries, then input this dataset into the function to return summary statistics for life expectancy in Europe.
```{r}
gap_Europe <- gapminder %>%
  filter(continent == "Europe")

summary_stats(gap_Europe$lifeExp)
```
*Exercise 4: Test the Function*

These are the tests for my summary_statistics function.    
```{r}
test_that("Testing summary statistics function",{
  expect_equal(summary_stats(adelie$bill_length_mm), c(max(adelie$bill_length_mm) - min(adelie$bill_length_mm), mean(adelie$bill_length_mm), median(adelie$bill_length_mm))) 
          })
```
```{r}
test_that("Testing summary statistics no error",{
  expect_no_error(summary_stats(gapminder$lifeExp)) 
          })
```
```{r}
test_that("Testing summary statistics error message",{
  expect_error(summary_stats(gapminder$country), "Input is not of class numeric: Input must be of class numeric") 
          })
```
```{r}
test_that("Testing summary statistics return length",{
  expect_length(summary_stats(gapminder$lifeExp), 3) 
          })
```

